Modelling last glacial cycle ice dynamics in the Alps

### 2017-11-21 articles/cycle/alps-cycle.tex
Embed word counts in Alps cycle manuscript.
Move methods and climate forcing after main.
Mask sections planned for removal.
Restore sideways figures orientation to portrait.
Move supplementary figures and tables apart.
Combine timing, trimlines and profiles figures.

@@

\definecolor{darkblue}{cmyk}{0.9,0.3,0.0,0.0}
\definecolor{darkgreen}{cmyk}{0.8,0.0,1.0,0.0}
\definecolor{darkred}{cmyk}{0.1,0.9,0.8,0.0}
\definecolor{darkorange}{cmyk}{0.0,0.5,1.0,0.0}
\definecolor{darkpurple}{cmyk}{0.6,0.7,0.0,0.0}
\definecolor{darkbrown}{cmyk}{0.23,0.73,0.98,0.12}

\newcommand{\idea}[1]{\textcolor{darkgreen}{\emph{[\textbf{IDEA:} #1]}}}
\newcommand{\note}[1]{\textcolor{darkblue}{\emph{[\textbf{NOTE:} #1]}}}
\newcommand{\todo}[1]{\textcolor{darkred}{\emph{[\textbf{TODO:} #1]}}}
\newcommand{\aref}[0]{\textcolor{darkblue}{\textbf{[REF.]}}}

@@

@@

% ----------------------------------------------------------------------
%TC: break Introduction
\introduction
\label{sec:intro}
% ----------------------------------------------------------------------

@@

@@

@@

% ----------------------------------------------------------------------
\section{Ice sheet model set-up}
\label{sec:model}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\section{Palaeo-climate forcing}
\label{sec:climate}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\section{Results and discussion}
\label{sec:results}
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
%TC: break Conclusions
\conclusions
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
%TC: break Acknowledgements
% Acknowledgements
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
%TC: break References
% References
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
%TC: break Figures
% Figures
\clearpage
% ----------------------------------------------------------------------

@@

    \begin{sidewaysfigure*}
      % scalebox is not necessary in production mode
      \centerline{\scalebox{0.9}{\includegraphics{alpcyc_hr_lgmvel}}}
      \caption{%
        \textbf{(a)} Modelled bedrock topography (grey), ice surface topography
        (200\,m contours), and ice surface velocity (blue) in the Alps
        24.57\,ka before present, corresponding to the maximum modelled ice
        cover. Modelled self-sustained ice domes (triangles) and some major
        transfluences (crosses) are shown. Modelled LGM
        ice extent (dashed orange line) and geomorphological
        reconstruction \citep[solid red line,][]{Ehlers.etal.2011}. The
        background map consists of depressed SRTM \citep{Jarvis.etal.2008}
        topography and Natural Earth Data \citep{Patterson.Kelso.2017}.
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model \citep[black
        curve,][]{Jouzel.etal.2007}, and modelled total ice volume through the
        last glacial cycle (120--0\,ka), expressed in meters of sea level
        equivalent (m~s.l.e., blue curve). Gray fields indicate Marine
        Oxygen Isotope Stage (MIS) boundaries for MIS~2 and MIS~4 according to
        a~global compilation of benthic \chem{\delta^{18}O} records
        \citep{Lisiecki.Raymo.2005}.}
      \label{fig:lgmvel}
    \end{sidewaysfigure*}

    \begin{sidewaysfigure*}
      % scalebox is not necessary in production mode
      \centerline{\scalebox{0.9}{\includegraphics{alpcyc_hr_timing}}}
      \caption{%
        \textbf{(a)} Timing of the LGM given by the modelled age of maximum ice
        thickness throughout the entire simulation (colour mapping) and
        corresponding, ice surface elevation (200\,m contours).
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model (black curve),
        and modelled glacierized area during the LGM (coloured curve). The LGM
        is here modelled as a time-transgressive event.}
      \label{fig:timing}
    \end{sidewaysfigure*}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{%
        \textbf{(a)} Comparison of modelled ice surface elevation at the LGM
        (time-transgressive, corresponding to maximum ice thickness,
        Fig.~\ref{fig:timing}), compensated for bedrock deformation, against
        observed trimline elevations \citep[Table~1]{Kelly.etal.2004}. Colours
        show the age of maximum ice thickness (as in Fig.~\ref{fig:timing}).
        Model variables were bilinearly interpolated to the trimline locations.
        \textbf{(b)} Histogram of differences between modelled LGM ice surface
        elevation and trimline elevations (500\,m bands). The average
        difference is 861\,m.
        \textbf{(c)} Observed upper Rhone valley trimline locations
        \citep[Table~1]{Kelly.etal.2004}, modelled age of maximum ice thickness
        (colour) and LGM ice surface elevation (200\,m contours). Hatches
        mark areas modelled to have experienced less than 1\,ka temperate ice
        cover during MIS~2 (29--14\,ka).}
      \label{fig:trimlines}
    \end{figure}

    \begin{figure*}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{%
        \textbf{(a, c, e, g, i, k)} Profile lines roughly following valley
        centerlines for the Rhine, Rhone, Dora Baltea and Isère, Inn and
        Tagliamento Glaciers.
        \textbf{(b, d, f, h, j, l)} Evolution of modelled glacier extent in
        time, bilinearly interpolated along the corresponding profiles, showing
        numerous cycles of advance and retreat over the last glacial cycle
        modulated by subglacial topography and catchment geometry.
        Isolated patches indicate periodic surges from tributary glaciers.}
      \label{fig:profiles}
    \end{figure*}

% ----------------------------------------------------------------------
% Tables
\clearpage
% ----------------------------------------------------------------------

>>>>

\usepackage{framed}
\usepackage{verbatim}

@@

\definecolor{gray}{gray}{0.75}
\definecolor{darkblue}{cmyk}{0.9,0.3,0.0,0.0}
\definecolor{darkgreen}{cmyk}{0.8,0.0,1.0,0.0}
\definecolor{darkred}{cmyk}{0.1,0.9,0.8,0.0}
\definecolor{darkorange}{cmyk}{0.0,0.5,1.0,0.0}
\definecolor{darkpurple}{cmyk}{0.6,0.7,0.0,0.0}
\definecolor{darkbrown}{cmyk}{0.23,0.73,0.98,0.12}

\newcommand{\idea}[1]{\textcolor{darkgreen}{\emph{[\textbf{IDEA:} #1]}}}
\newcommand{\note}[1]{\textcolor{darkblue}{\emph{[\textbf{NOTE:} #1]}}}
\newcommand{\todo}[1]{\textcolor{darkred}{\emph{[\textbf{TODO:} #1]}}}
\newcommand{\aref}[0]{\textcolor{darkblue}{\textbf{[REF.]}}}
\newenvironment{mask}{\color{gray}}{\color{black}}
%TC:newcounter mask
%TC:envir mask [] mask

@@

% Texcount template
%TC:newtemplate
%TC:template Word counts (text (masked), headers, other):\n
%TC:template  {SUB?* {title}: {text} ({mask}), {headerword}, {otherword}\n?SUB}
%TC:template Total: {text} ({mask}), {headerword}, {otherword}

\begin{framed}
\small\verbatiminput{alps-cycle.sum}
\end{framed}

@@

% ----------------------------------------------------------------------
\section{Main}
\label{sec:intro}
% ----------------------------------------------------------------------

@@

    \begin{mask}

@@

    \end{mask}

@@

    \begin{mask}

% ----------------------------------------------------------------------
\subsection{Results and discussion}
\label{sec:results}
% ----------------------------------------------------------------------

    \end{mask}

    \begin{mask}

    \end{mask}

    \begin{mask}

    \end{mask}

    \begin{mask}

    \end{mask}

    \begin{mask}

    \end{mask}

    \begin{mask}

% ----------------------------------------------------------------------
\subsection{conclusions}
% ----------------------------------------------------------------------

    \end{mask}

% ----------------------------------------------------------------------
\section{Methods}
\label{sec:model}
% ----------------------------------------------------------------------

@@

% ----------------------------------------------------------------------
\section{Supplementary}
\label{sec:climate}
% ----------------------------------------------------------------------

@@

%TC:break Acknowledgements
% ----------------------------------------------------------------------
% Acknowledgements
% ----------------------------------------------------------------------

@@

%TC:break References
% ----------------------------------------------------------------------
% References
% ----------------------------------------------------------------------

@@

%TC:break Figures
% ----------------------------------------------------------------------
% Figures
\clearpage
% ----------------------------------------------------------------------

    \begin{figure*}
      \centerline{\includegraphics{alpcyc_hr_lgmvel}}
      \caption{%
        \textbf{(a)} Modelled bedrock topography (grey), ice surface topography
        (200\,m contours), and ice surface velocity (blue) in the Alps
        24.57\,ka before present, corresponding to the maximum modelled ice
        cover. Modelled self-sustained ice domes (triangles) and some major
        transfluences (crosses) are shown. Modelled LGM
        ice extent (dashed orange line) and geomorphological
        reconstruction \citep[solid red line,][]{Ehlers.etal.2011}. The
        background map consists of depressed SRTM \citep{Jarvis.etal.2008}
        topography and Natural Earth Data \citep{Patterson.Kelso.2017}.
        \textbf{(b)} Temperature offset time-series from the EPICA ice core
        used as palaeo-climate forcing for the ice flow model \citep[black
        curve,][]{Jouzel.etal.2007}, and modelled total ice volume through the
        last glacial cycle (120--0\,ka), expressed in meters of sea level
        equivalent (m~s.l.e., blue curve). Gray fields indicate Marine
        Oxygen Isotope Stage (MIS) boundaries for MIS~2 and MIS~4 according to
        a~global compilation of benthic \chem{\delta^{18}O} records
        \citep{Lisiecki.Raymo.2005}.}
      \label{fig:lgmvel}
    \end{figure*}

    \begin{figure*}
      \centerline{\includegraphics{alpcyc_hr_dynamics}}
      \caption{%
        \textbf{(a)} Timing of the LGM given by the modelled age of maximum ice
        thickness throughout the entire simulation (colour mapping) and
        corresponding, ice surface elevation (200\,m contours). Observed upper
        Rhone valley trimline locations \citep[black dots;][Table~1]
        {Kelly.etal.2004} and areas modelled to have experienced
        less than 1\,ka temperate ice cover during MIS~2 (29--14\,ka, hatches).
        The LGM is here modelled as a time-transgressive event. Profile lines
        roughly following valley centerlines for the Rhine and Inn Glaciers.
        \textbf{(b)} Comparison of modelled ice surface elevation at the LGM
        (time-transgressive, corresponding to maximum ice thickness,
        Fig.~\ref{fig:timing}), compensated for bedrock deformation, against
        observed trimline elevations \citep[Table~1]{Kelly.etal.2004}. Colours
        show the age of maximum ice thickness (as in Fig.~\ref{fig:timing}).
        Model variables were bilinearly interpolated to the trimline locations.
        \textbf{(c)} Evolution of modelled glacier extent in
        time, bilinearly interpolated along the Rhine and Inn profiles, showing
        numerous cycles of advance and retreat over the last glacial cycle
        modulated by subglacial topography and catchment geometry.
        Isolated patches indicate periodic surges from tributary glaciers.}
      \label{fig:timing}
      \label{fig:trimlines}
      \label{fig:profiles}
    \end{figure*}

%TC:break Supplementary figures
% ----------------------------------------------------------------------
% Supplementary figures
\clearpage
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
% ----------------------------------------------------------------------

@@

%TC:break Supplementary tables
% ----------------------------------------------------------------------
% Supplementary tables
\clearpage
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
% ----------------------------------------------------------------------
